### 2020-06-01 paper.tex
Add a Missing Period In the Related Work Section

Let $d_{h}^{ij}$ $d_{v}^{ij}$ be the horizontal and the vertical distance between cell $i$ and its $j^{th}$ out cell respectively, the total wire length of the chip can be expressed as the following equation 
\begin{equation}
    C_{1} = \sum_{i=cell}^{n} \sum_{j=out cell}^{n} (d_{h}^{ij} + d_{v}^{ij})
\end{equation}
Where $n$ is the total number of cells in the chip 
In case of the second term $C_{2}$, whenever two cells are swapped, they might overlap, therefore, $O_{ij}$ indicates the overlap between cell $i$ and cell $j$, this overlap is undesirable and it negatively affects the cost function by increasing its value by the term $C_{2}$ which is the summation of each overlap value squared.
\begin{equation}
    C_{2} = \sum_{i!=j} (O_{ij}^{2})
\end{equation}
The cost function is calculated at each iteration after generating a new cells layout.
\medskip

>>>>

Let $d_{h}^{ij}$ $d_{v}^{ij}$ be the horizontal and the vertical distance between cell $i$ and its $j^{th}$ out cell respectively, the total wire length of the chip can be expressed as the following equation 
\begin{equation}
    C_{1} = \sum_{i=cell}^{n} \sum_{j=out cell}^{n} (d_{h}^{ij} + d_{v}^{ij})
\end{equation}
Where $n$ is the total number of cells in the chip. In case of the second term $C_{2}$, whenever two cells are swapped, they might overlap, therefore, $O_{ij}$ indicates the overlap between cell $i$ and cell $j$, this overlap is undesirable and it negatively affects the cost function by increasing its value by the term $C_{2}$ which is the summation of each overlap value squared.
\begin{equation}
    C_{2} = \sum_{i!=j} (O_{ij}^{2})
\end{equation}
The cost function is calculated at each iteration after generating a new cells layout.
\medskip
